The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-19 analysis/paper/paper.qmd
Update topic model text

# 
emu_theses_topics <- tidy(emu_theses_lda, matrix = "beta")
emu_theses_topics

# The top 10 words that are the most coomon in each topic
emu_theses_top_terms <- emu_theses_topics |> 
  group_by(topic) |> 
  top_n(10, beta) |> 
  ungroup() |> 
  arrange(topic, -beta)

>>>>

# Tidy model with beta statistic
emu_theses_topics <- tidy(emu_theses_lda, matrix = "beta")
emu_theses_topics

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- emu_theses_topics |> 
  group_by(topic) |> 
  top_n(10, beta) |> 
  ungroup() |> 
  arrange(topic, -beta)
